\documentclass[oneside, 11pt]{article}
\usepackage{xeCJK} % Support for CJK texts
\usepackage{fontspec}
\usepackage[letterpaper]{geometry} % Geometry (or a4paper)
\usepackage{multicol} % Flexibility in columns
\usepackage[shortlabels]{enumitem} % Better enumerate
\usepackage[hidelinks]{hyperref} % Hyperref
\usepackage[parfill]{parskip} % Skip ahead, not indent

\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{ragged2e}
\usepackage{calc}
% \usepackage[fira]{fontsetup}

% geometry
\geometry{margin=0.5in}

% hyperref setup
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue
}

% Resume Macros/Commands
\newcommand*{\experienceEntry}[4]{
	\noindent
	\begin{tabularx}{\textwidth}{Xr}
	\textbf{#1},\quad #2 & #3\\
	#4
	\end{tabularx}
	\vspace{-0.75\baselineskip}
}

\newcommand*{\projectEntry}[3]{
	\noindent
	\begin{tabularx}{\textwidth}{Xr}
	\textbf{#1} -- #3 & #2
	\end{tabularx}
	\vspace{-1.25\baselineskip}
}

\newenvironment{expD}
	{\begin{itemize}[noitemsep,topsep=0pt]}
	{\end{itemize}}

\newenvironment{expDS}
	{\begin{itemize}[noitemsep,topsep=0pt,label={}]}
	{\end{itemize}}

% Customize section headings
\titleformat{\section}
	{\normalfont\large\bfseries\sffamily} % Text style: normal font, large size, bold, italic
	{\thesection}                        % Section number
	{1em}                                % Space between number and title
	{}                                   % Code before title
	[\titlerule]

\titlespacing*{\section}
	{0pt}                                % Left margin
	{1em}                                % Space before (vertical space)
	{0.5em}                                % Space after (vertical space)



\begin{document}

% Name & Contact
\begin{center}
	\Large \textbf{Martin Weiqi Gong 龚炜棋}\\
	\normalsize \href{mailto:martingwq@hotmail.com}{martingwq@hotmail.com} \thinspace \textbf{|} \thinspace +1 857-296-2860 \thinspace +86 13530769122
\end{center}

\section*{Education}

\experienceEntry{University of Southern Califorinia}
	{Los Angeles, CA}
	{2023 -- Present}
	{B.S. in Physics, B.S. in Computer Science Games \quad GPA: 3.93}

\experienceEntry{Deerfield Academy}
	{Deerfield, MA}
	{2019 -- 2023}
	{High School Diploma with High Honors/Excellence in Computer Science \quad GPA: 3.85}

\section*{Coursework}

\begin{tabular}{ p{\textwidth - 1em} }
	Linear Algebra, Differential Equations, Multi-Variable Calculus, Mechanics, Electromagnetism, Data Structures \& Algorithms.
\end{tabular}

\section*{Skills}

\begin{tabularx}{\textwidth}{rX}
	\textit{Coding:} & C++, Python, Java, Verilog, PHP, HTML, CSS, TypeScript, JavaScript, Arduino, Handlebars\\
	\textit{Tech/Env:} & \LaTeX, Shell, Git, Makefile, TensorFlow, PyGame, Matplotlib, React, Node.js, Windows, Linux, macOS\\
	\textit{Software:} & Adobe Suite, AutoCAD, Mathematica, SolidWorks, KiCAD\\
	\textit{Languages:} & Chinese(Fluent), English(Fluent), Spanish(Basic), Japanese(Basic)
\end{tabularx}


\section*{Experience}

\experienceEntry{EZfun Interactive Technology Ltd.}
	{Shenzhen, China}
	{Jun -- Aug 2023}
	{Student Intern}

\begin{expD}
	\item Created and optimize the Localization of the English mobile version of \textit{Dynasty Warriors}
	\item Optimized in-game audio and fine-tuned game mechanics in Unity for WeChat minigame.
\end{expD}

\experienceEntry{Kaggle}
	{Online}
	{Jul 2022 -- Jun 2023}
	{Contestant}

\begin{expD}
	\item Group participation in training and testing computer vision model (CNN) using TensorFlow.
\end{expD}

\experienceEntry{First Tech Challenge}
	{Deerfield, MA}
	{Aug 2018 -- Apr 2023}
	{Team Leader; Mechanical Design and Robot Programming}

\begin{expD}
	\item Visual pattern and object recognition and autonomous robot operation logic in Java using OpenCV and TensorFlow Lite.
	\item Mechanical design of task specific retrieval/placement mechanisms and wheeled chasis.
	\item CAD modeling of robot design in SolidWorks with custom and standard parts.
\end{expD}

\section*{Projects}

\projectEntry{Website and Web Service}
	{2019 -- Present}
	{Personal website and API maintenance}

\begin{expD}
	\item Build and maintain websites using PHP, React, Bootstrap, and Nginx. Maintain blog using Ghost CMS.
	\item Build custom APIs using node.js to cache/serve testing applications and learning projects.
	\item Route and maintain proxied servers for computer games using openVPN.
\end{expD}

\projectEntry{Geiger Counter}
	{Spring 2023}
	{Geiger counter based on FPGA.}

\begin{expD}
	\item Program FPGA to handle analog rising edges of the Geiger tube.
	\item Concurrent control of different devices (buzzer) with single clock
	\item Design and optimization of high-voltage circuits
\end{expD}

\projectEntry{Analysis of Soft-Tip Mechanical Fingers}
	{Summer 2022}
	{Statistical analysis of the effectiveness for each.}

\begin{expD}
	\item Statistical/mathematical modeling of kinematics of mechanical fingers using python and demonstrated with matplotlib.
	\item CAD designing of experimentation apparatus with interchangeable mechanical tips. Manufacture apparatus through 3D printing and laser cutting.
\end{expD}

\projectEntry{Eye Tracking Page Flipper}
	{Summer 2021}
	{Page flipping for disabled/performers}

\begin{expD}
	\item Utilize OpenCV to track and locate relative position of the iris with edge detection and center of mass algorithms
	\item Physical modeling and design of pressure based page flipping device for physical pages
\end{expD}

\end{document}